Redundant calibration as a complex optimization problem

### 2017-02-24 paper.tex
started implementing Gianni's suggestions

Eq.~\eqref{eq:vis_definition} can also be expressed in the following vector form 
\begin{equation}
\label{eq:vis_definition}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= v_{pq}=g_p y_{pq} \conj{g_q},\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
The function $\alpha_{pq}$ maps composite antenna indexes to unique single indexes and is defined as
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
%B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
For example,
\begin{equation}
\{\alpha_{12},\alpha_{13},\alpha_{1N},\alpha_{23},\cdots,\alpha_{N-1N}\} = \{1,2,N-1,N,\cdots,B\},
\end{equation}
where $B$ denotes the number of baselines in the array, i.e. $B = \frac{N^2-N}{2}$. The vectors in Eq.~\eqref{eq:vec_definitions} are column vectors of size $B$ (i.e. $p<q$).

We can now formulate calibration as a least-squares problem:
\begin{equation}
\label{eq:least_squares}
\min_{\bg} \Lambda(\bg) = \min_{\bg} \|\br\|_F^2 = \min_{\bg} \|\bd - \bv(\bg)\|_F^2, 
\end{equation}
where $\bg =[g_1,\cdots,g_N]^T$.

least squares problems are normally solved by using gradient based methods, like Gauss-Newton and Levenberg-Marquardt .

>>>>

Eq.~\eqref{eq:vis_definition} can also be expressed in the following vector form 
\begin{equation}
\label{eq:vis_definition}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= v_{pq}=g_p y_{pq} \conj{g_q},\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
The function $\alpha_{pq}$ maps composite antenna indexes to unique single indexes and is defined as
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
%B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
For example, the set
\begin{equation}
\{\alpha_{12},\alpha_{13},\cdots,\alpha_{1N},\alpha_{23},\cdots,\alpha_{N-1N}\}
\end{equation}
and the set
\begin{equation}
\{1,2,\cdots,N-1,N,\cdots,B\},
\end{equation}
are equal. We denote the number of baselines in an array with $B$, i.e. $B = \frac{N^2-N}{2}$. The vectors in Eq.~\eqref{eq:vec_definitions} are column vectors of size $B$ (i.e. $p<q$).

We can now formulate calibration as a least-squares problem:
\begin{equation}
\label{eq:least_squares}
\min_{\bg} \Lambda(\bg) = \min_{\bg} \|\br\|_F^2 = \min_{\bg} \|\bd - \bv(\bg)\|_F^2, 
\end{equation}
where $\bd$ is the observed visibility vector, $\bv$ is the model predicted visibility vector and $\bg =[g_1,\cdots,g_N]^T$.
In

Least-square type problems are generally solved by using gradient based minimization algorithms. In this paper we will be focusing on the following gradient minimization algorithms: GN and LM \citep{Levenberg1944,Marquardt1963}.
To employ gradient based algorithms the objective function of a least-squares problem has to be differentiable with respect to the model parameters, which in the case of 
Eq.~\ref{eq:least_squares} is
